Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-12 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Optimization Analysis}

For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm parameters (continuous input variables) are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. The algorithm's initial values are chosen to be in the center of the design space, namely, $\lambda=1$ and diagonal separation$=0.5*L$. The covariance matrix is initialized uniformly with standard deviation \mf{ADD HERE}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{Caption}
    \label{BucklingOptimization}
\end{figure}

>>>>

\section{Optimization Analysis}
For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm parameters (continuous input variables) are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. The algorithm's initial values are chosen to be in the center of the design space, namely, $\lambda=1$ and diagonal separation$=0.5*L$. The covariance matrix is initialized uniformly with standard deviation \mf{ADD HERE}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary. }
    \label{BucklingOptimization}
\end{figure}
